Applicability of SSM and UML for Designing a Search Application for the British Broadcasting Corporation (BBC)

### 2014-03-31 paper.tex
Added some more detail around the goal of the paper based on peer review from submission to EMMSAD.

@@

The purpose of this paper is to start the high-level design -- and
look at the lower levels of one or two aspects -- of a search application
specific to BBC content. The intent is to provide a consistent user interface
that allows the audience to find news articles, sport results,
TV catch-up, education resources and everything else the BBC produces.

@@

@@

@@

Having extracted the activities that appear to pertain to the
search application directly (and the actors involved in those activities),
we can produce the use case UML diagram shown in Fig.~\ref{use-case}.

This illustrates only a subset of the expected behaviours for a full
BBC search application, but touches on some of the diversity of the
potential uses. For the purposes of our initial design, we can next look
into defining the system behaviour for some of these use cases.

@@

Figure~\ref{sequence-producer}
shows how a TV producer indirectly interacts with search by providing
information that ultimately ends up in the search indexes and
Fig.~\ref{sequence-user} shows a sequence diagram defining a user
interacting with the search system

>>>>

\subsection{Design Goals}

The purpose of this paper is to explore how contextualisation through SSM
and then using UML to form a high-level design might benefit building a
hypothetical, new search application for the BBC.
The hope is that insights from
fresh analysis and design might form suitable proposals for potential
improvements and development within the existing application.
These approaches might also lead to further work to evaluate the
current application by highlighting where the BBC Search application
differs from an ``ideal'' model (if it can be described as such) derived from 
such a redesign with a contemporary view of the problem space.

Ultimately, any organisation like the BBC is unlikely to replace a large
application atomically, but is likely to migrate over time to
its ``ideal'' form with smaller, iterative improvements. It is proposed
that there is some value in designing what that ``ideal'' form might
be so as to provide proposals for those improvements.

@@

@@

This rich picture was created using domain knowledge dervied from the existing
search system and technical knowledge of the BBC websites. If the initial
designs from this paper prove promising in practice, the authors would
recommend repeating the exercise with a broader range of stakeholders
and domain experts from respective subsystems. A rich picture does not
have to serve as authoritative snapshot of the problem space, but can
instead been seen as a collaborative exercise between stakeholders. Such
contextualisation is likely worth iterating over time as the industry
changes, e.g. the recent shift from separate mobile websites to
\emph{Responsive Design}\cite{marcotte2010responsive} might change
the understanding around mobile devices.

@@

In other words, we can say
that editorial staff and content editors might be seen as direct
users of the system, with actors, presenters, etc. seen as meta-level
users. This is justified by noting that journalists and editorial staff
will have their content exactly as typed appear in search results, but
production staff behind television and radio programming contribute
only indirectly to the search system. They produce the content that users
will later wish to see, but they have little contribution to the
discovery of that content later on.

This follows from the
Interactive Management approach from Dogan and Henshaw\cite{dogan2010transition}
and is still largely subjective. For example, if a journalist
publishes to a content management system, with which a search
system then integrates without their knowledge, can they still
be considered to be a direct user of the search system? In this
design we argue that such syndication into the search system means
their actions (e.g. to publish, remove, update articles) will
have direct effect on the search and discovery of those
articles (e.g. they may become searchable, cease being searchable
or start being searchable under new criteria) and thus they are
direct users of the search system. It is recognised however, that
a more collaborative rich picture drawn up with a wider set
of stakeholders might lead to a different opinion.

@@

Having extraced the direct users only of the search system, further
requirements-gathering and business analysis can define their
respective use cases of the system. An analysis based on domain
knowledge from the existing search system leads to the
use case UML diagram shown in Fig.~\ref{use-case}.

This illustrates only a subset of the expected behaviours for a full
BBC search application, but touches on some of the diversity of the
potential uses. For the purposes of our initial design, we can next look
into defining the system behaviour for some of these use cases. It should
be noted that these are illustrative of the breadth of use cases, but
deeper business analysis and creation of corresponding use cases
(perhaps following the style of Cockburn\cite{cockburn2001writing})
should be performed as part of a more in-depth study before the
high-level design can be truly considered complete and valid.

@@

The breadth of content the search system will need to index and retrieve
sits across multiple systems within the BBC (e.g. programme metadata
lives in a distinct location to news articles). The diversity of
systems, formats and metadata involved suggested approaching the
more functional design as a classic \emph{Enterprise Integration}
problem\cite{brosey2001grand}.

Figure~\ref{sequence-producer}
shows how a TV producer indirectly interacts with search by providing
information that ultimately ends up in the search indexes and
Fig.~\ref{sequence-user} shows a sequence diagram defining a user
interacting with the search system.
